Evaluating effects of light quality: A basis for selecting the spectral photon flux density distribution of light for measuring photosynthetic rates of leaves

### 2016-08-04 NotUsed/Sup1.Rmd
英文構成を依頼 (Edanz)。3089 words

```{r Spectra, eval = evalFig}

# set integrate ranges
PFD_integrate_min <- 350
PFD_integrate_max <- 750

IntegratePFD <- 100

panel_names <- c("(A) HIDs and fluorescent lamps", "(B) LEDs", "(C) Incident and leaf transmitted sunlight")

# HID_raw <-
#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
# 
# HIDs <-
#   HID_raw %>%
#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
#   select(1, HPS_ = 12, MH_ = 21)
FL_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_FL.csv") %>%
  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
  na.omit

FL_Ocean_PFD <-
  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

FL_Ocean <-
  FL_Ocean_raw %>%
  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")

HPS_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
  rename(wavelength = V1, value = V2)

HPS_Ocean_PFD <-
  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

HPS_Ocean <-
  HPS_Ocean_raw %>%
  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")

MH_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
  rename(wavelength = V1, value = V2)

MH_Ocean_PFD <-
  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

MH_Ocean <-
  MH_Ocean_raw %>%
  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")

OceanSPDs <-
  bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
  mutate(panel = panel_names[1])

Absorptances <-
  fread("~/Dropbox/materials/SpectrumCucumber.csv") %>%
  filter(Trtm %in% c("W", "WFR", "FL")) %>%
  mutate(wavelength = as.numeric(wavelength)) %>%
  filter(variable == "absorption", Trtm == "W")

Sun <-
  fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
  setnames(c("wavelength", "Sunlight")) %>%
  left_join(., Absorptances, by = "wavelength") %>%
  transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)

# Sun: JIS C8904-3

LEDs <-
  fread("~/Dropbox/materials/SPD_FL.csv") %>%
  transmute(wavelength = `Wavelength[nm]`, W, FR, B = B_HL, R = R_SR) %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[2]) %>%
  na.omit

SPD_labels <-
  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 700),
             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf transmitted sunlight"),
             panel = rep(panel_names,  c(3, 4, 2)))

SPDs <-
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[3]) %>%
  bind_rows(., OceanSPDs, LEDs) %>%
  filter(between(wavelength, 380, 820)) %>%
  # ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
  theme_bw2() +
  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
  geom_line() +
  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
  # scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey50", "black", "black")) +
  # facet_grid(panel ~ .) +
  facet_wrap(~ panel, ncol = 1) +
  gg_xy(c(380, 820, 0, 4.5)) +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

CapSPD <-
  "Fig. S1  The spectral photon flux density distributions of light provided by (A) high-intensity discharge lamps (HIDs) and fluorescent lamps, (B) light-emitting diodes (LEDs), and (C) incident and leaf transmitted sunlight (see also Table S1). The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown. The distribution of sunlight was adopted from JIS C 8904-3. The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016). The far-red waveband (700--750 nm) is filled in grey."
```

@@

```{r FigSPD, eval = evalFig, fig.cap = CapSPD}
SPDs
```

Table S1.  Description of the light sources and the instruments used for the measurements of the spectral photon flux density distributions.

| Light source (abbreviation)     | Model code                    | Measuring instrument              |
|:--------------------------------|:------------------------------|:----------------------------------|
| Fluorescent lamp (FL)           | FPL55EX-N<sup>\*1</sup>       | HR2000 (Ocean Optics Inc.)        |
| Metal halide lamp (MH)          | M220FCELS-W/BUD<sup>\*1</sup> | HR2000 (Ocean Optics Inc.)        |
| High-pressure sodium lamp (HPS) | NH220FLS<sup>\*1</sup>        | HR2000 (Ocean Optics Inc.)        |
| Blue LED (B)                    | HBL3-3S55-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
| Red LED (R)                     | SRK3-3A80-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
| Far-red LED (FR)                | L735-36AU<sup>\*3</sup>       | MS-720 (EKO Instruments Co. Ltd.) |
| White LED (W)                   | NSPW310DS<sup>\*4</sup>       | MS-720 (EKO Instruments Co. Ltd.) |

^\*1^IWASAKI ELECTRIC CO., LTD., Tokyo, Japan; ^\*2^Tricon Co., Shimane, Japan; ^\*3^Epitex Inc., Kyoto, Japan; ^\*4^Nichia Chemical Industries Ltd., Tokushima, Japan.

>>>>

@@

<!-- Table S1.  Description of the light sources and the instruments used for the measurements of the spectral photon flux density distributions.  -->

<!-- | Light source (abbreviation)     | Model code                    | Measuring instrument              | -->
<!-- |:--------------------------------|:------------------------------|:----------------------------------| -->
<!-- | Fluorescent lamp (FL)           | FPL55EX-N<sup>\*1</sup>       | HR2000 (Ocean Optics Inc.)        | -->
<!-- | Metal halide lamp (MH)          | M220FCELS-W/BUD<sup>\*1</sup> | HR2000 (Ocean Optics Inc.)        | -->
<!-- | High-pressure sodium lamp (HPS) | NH220FLS<sup>\*1</sup>        | HR2000 (Ocean Optics Inc.)        | -->
<!-- | Blue LED (B)                    | HBL3-3S55-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) | -->
<!-- | Red LED (R)                     | SRK3-3A80-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) | -->
<!-- | Far-red LED (FR)                | L735-36AU<sup>\*3</sup>       | MS-720 (EKO Instruments Co. Ltd.) | -->
<!-- | White LED (W)                   | NSPW310DS<sup>\*4</sup>       | MS-720 (EKO Instruments Co. Ltd.) | -->

<!-- ^\*1^IWASAKI ELECTRIC CO., LTD., Tokyo, Japan; ^\*2^Tricon Co., Shimane, Japan; ^\*3^Epitex Inc., Kyoto, Japan; ^\*4^Nichia Chemical Industries Ltd., Tokushima, Japan. -->
